---
title: "Study Questions - Lecture 18"
author: "Your name here"
date: "2023-02-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Q1. During an hour, you measure air temperature T every 10 minutes according the table below. Calculate the terms below:

| Minutes | T (Celsius) | 
| :------ |------------:| 
| 10      | 12.6        |
|20       | 11.2        |
|30       | 11.9        |
|40       | 13.1        |
|50       | 12.0        |
|60       | 11.8        |


```{r}
#Fi{r}st create dataframe
minutes <- c(10,20,30,40,50,60)
temperature <- c(12.6,11.2,11.9,13.1,12.0,11.8)
data <- data.frame(minutes,temperature)

# Now display output
head(data)
```

a) Calculate $\overline{T}$


```{r}
# You can calcute average temperature using the equation on slide 7 in Lecture 18 or using the the mean function

# Let's try calculating average temperature using the equation on slide 7 in Lecture 18
Tbar <- 1/6*(12.6+11.2+11.9+13.1+12.0+11.8)

# Display output
cat("average temperature is: ", Tbar, intToUtf8(176), "C", "\n")

# Now let's calculate average temperature using the average function
Tbar2 <- mean(data$temperature)

# Display output
cat("average temperature is: ", Tbar2, intToUtf8(176), "C", "\n")

# We can see that the results are the same
```

b) T' at 40 min


```{r}
# First we need to calculate deviations in temperature
data$Tprime <- data$temperature-Tbar

# Display output
head(data)

# From this table you can estimate T' at 40 min
cat("T' at 40 min is: ", data$Tprime[4], intToUtf8(176), "C", "\n") #data$Tprime[4] mean you're taking the 4th value of Tprime 

```

c) T$^{'2}$ at 20 min


```{r}
# Again we can estimate that from the dataframe above (i.e. you'll need to squate T' at 20 min)
Tprime_squared <- data$Tprime[2]^2

# Display output
cat("T'2 at 30 min is: ", Tprime_squared, intToUtf8(176), "C2", "\n") #data$Tprime[4] mean you're taking the 4th value of Tprime 
```

d) $\overline{T^{'}}$


```{r}
# By default this term should be zero, but we can check this using the following
Tprime_mean <- 1/6*sum(data$Tprime)
Tprime_mean <- mean(data$Tprime)

# Display output
cat("The average deviation in T is: ", round(Tprime_mean,10), intToUtf8(176), "C", "\n")
```

e) $\overline{T^{'2}}$


```{r}
# This is the the variance of the time series of T. We can calculate it as follows
Tprime_squared_mean <- 1/6*sum(data$Tprime^2)
Tprime_squared_mean <- mean(data$Tprime^2)

# Display output
cat("the the variance of the time series of T is: ", round(Tprime_squared_mean,2), intToUtf8(176), "C2", "\n")
```

f) $\overline{T^{'}}^{2}$


```{r}
# Again by default this term should be zero, but we can check this using the following
Tprime_mean_squared <- mean(data$Tprime)^2

# Display output
cat("mean T' is: ", round(Tprime_mean_squared,10), intToUtf8(176), "C", "\n")
```

Q2. See the handout for Study Questions - Lecture 18. This is best solved by hand

Q3. Calculate the following parameters if $\overline{u}$ = 4 m s$^{-1}$, $\overline{v}$ = 0 m s$^{-1}$, $\overline{w}$ = 0 m s$^{-1}$, $\sigma_{u}$ = 0.4 m s$^{-1}$, $\sigma_{v}$ = 0.2 m s$^{-1}$, and  $\sigma_{w}$ = 0.1 m s$^{-1}$

a) I$_{u}$


```{r}
# We can calculate the turbulence intensity as follows:
# First define the standard deviation
sigma_u <- 0.4

# Next estimate M
ubar <- 4
vbar <- 0
wbar <- 0
M <- sqrt(ubar^2+vbar^2+wbar^2)

# Now you can calculate the turbulence intensity
Iu <- sigma_u/M

# Display output
cat("Iu is: ", round(Iu,3), "\n")
```

b) I$_{w}$


```{r}
# define the standard deviation for w
sigma_w <- 0.1

# Next calculate the turbulence intensity
Iw <- sigma_w/M

# Display output
cat("Iw is: ", round(Iw,3), "\n")
```

c) $\overline{w^{'2}}$


```{r}
# Estimate this term using the standard deivation for w
variance_w <- sigma_w^2

# Display output
cat("The variance of w is: ", round(variance_w,3), "m2/s2", "\n")
```

d) $\overline{u^{'2}}$+$\overline{v^{'2}}$+$\overline{w^{'2}}$


```{r}
# Estimate this value using a similar calculation to that shown above
sigma_v <- 0.2
term <- sigma_u^2+sigma_v^2+sigma_w^2

# Display output
cat("This is equal to: ", round(term,3), "m2/s2", "\n")
```

 e) MKE/m


```{r}
# We can calculate mean kinetic energy (MKE) per unit mass (m) if we know the mean flow in the u,v, and w directions (which are define above)
MKE <- 1/2*(ubar^2+vbar^2+wbar^2)

# Display output
cat("The mean kinetic energy (MKE) per unit mass is: ", round(MKE,3), "m2/s2", "\n")
```

d) $\overline{e}$


```{r}
# The turbulent kinetic energy per unit mass can be estimate as:
e <- 1/2*term

# Display output
cat("The turbulent kinetic energy per unit mass is: ", round(e,3), "m2/s2", "\n")
```
