---
title: "Study Questions - Lecture 12"
author: "Your name here"
date: "2023-02-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# <center>University of British Columbia, Vancouver</center> 
## <center>GEOB 300 - Microscale Weather and Climate</center>  
### <center>Student Name, Student ID</center> 
```

Q1. How does the amplitude and phase lag of soil temperatures in a completely dry soil depend on (a) depth, and (b) soil organic matter content (at constant porosity)?


```{r}
# Enter anwer here an convert to Markdown after
```

Q2. Calculate the angular frequency for a diurnal ωd and an annual temperature wave ωa.


```{r}

```

Q3. Calculate the daily and annual damping depth D for a mineral soil with a thermal diffusivity κ = 5.0×10−7 m2 s−1. How do you interpret your results?


```{r}

```


```{r}
# How do you interpret your results? Enter answer here then convert to markdown
```

Q4. For the same soil, calculate when the soil temperature reaches its maximum at 5 cm if the maximum surface temperature is measured at 13:00?


```{r}
# the hms library will be helpful here
library(hms)

t1 <- as_hms("13:00:00")

z1 <- 
z2 <- 

# Calculate ∆t (dt)
dt <- 
dt <- hms(as.numeric(dt))

# Find when the soil temperature reaches its maximum at 5 cm
t2 <- dt+t1
t2 <- hms(as.numeric(t2))
         
# Display output
cat("Soil temperature reaches its maximum at 5 cm at: ", as.character(t2), "\n")        
```

Q5. In a different soil, you measure the daily maximum 5-cm soil temperature at 15:00 and the maximum 15-cm soil temperature at 18:00. Assume homogeneous soil properties and sinusoidal waves, and calculate the soil’s thermal diffusivity κ.


```{r}
# the hms library will be helpful here too
z1 <- 
z2 <- 

t1 <- as_hms("15:00:00")
t2 <- as_hms("18:00:00")

dt <- t1-t2

# hint went estimating thermal diffusivity, use as.numeric(dt)

```

Q6. Briefly compare the temperature regimes of mineral and organic soils.


```{r}
# Enter answer here then convert to markdown
```
